---
title: "Master Preprocessing Pipeline: E1 UG EEG (Face Phase)"
subtitle: "Face-locked P1, N170, EPN, LPP_face & ROI-Specific Baselines"
author: "Project Maintainer"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: show
    theme: flatly
---
``` {r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# ==============================================================================
# 1. Environment and Global Configuration
# ==============================================================================

if(!require("pacman")) install.packages("pacman")
if(!require("here")) install.packages("here")
pacman::p_load(tidyverse, reticulate, readr, stringr, here, fs)

# -----------------------------------------------------------
# Baseline configuration (following hu-neuro-pipeline docs)
# -----------------------------------------------------------
# use_baseline_correction:
#   TRUE  = apply baseline correction during preprocessing
#   FALSE = no baseline correction (baseline may be used later as covariate)
use_baseline_correction <- TRUE

# use_full_prestim_baseline:
#   TRUE  = use full pre-stimulus interval as baseline (c(NULL, 0.0))
#   FALSE = use conventional -200 to 0 ms baseline (c(-0.2, 0.0))
use_full_prestim_baseline <- FALSE

baseline_arg <- NULL
if (use_baseline_correction) {
  if (use_full_prestim_baseline) {
    # Full pre-stimulus interval as baseline
    baseline_arg <- c(NULL, 0.0)
  } else {
    # Conventional -200 to 0 ms baseline (default in hu-neuro-pipeline)
    baseline_arg <- c(-0.2, 0.0)
  }
} else {
  # No baseline correction at preprocessing stage
  baseline_arg <- NULL
}

# -----------------------------------------------------------
# Phase control
# -----------------------------------------------------------
# Face phase includes: P1, N170, EPN, and LPP_face
run_face_phase <- TRUE

# -----------------------------------------------------------
# Path definitions (relative paths via here() for portability)
# -----------------------------------------------------------

# 1. Input paths
path_py_pipeline_src <- here("python_modules", "hu-neuro-pipeline")
path_raw_eeg         <- here("data", "raw_all_cropped")
path_raw_log         <- here("data", "csv_all")

# 2. Intermediate log-processing paths
path_csv_filtered    <- here("data", "csv_filtered")
path_csv_summary     <- here("data", "csv_summaryPostRating")

# 3. Pipeline output root (heavy data such as epochs)
path_output_root     <- here("data", "pipeline_output")

# 4. Target paths for statistical analysis (face phase and baseline)
path_dest_face            <- here("data", "face_phase")                 # Face-locked ERP output
path_dest_baseline_face   <- here("data", "baseline", "LPP_face")       # Baseline for face-phase LPP

# Automatic directory creation
dirs_to_create <- c(
  path_csv_filtered, path_csv_summary, path_output_root,
  path_dest_face, path_dest_baseline_face
)
purrr::walk(dirs_to_create, ~dir.create(., showWarnings = FALSE, recursive = TRUE))
```

# 2. Python Environment Initialization and Pipeline Patch

``` {r python-init}
use_condaenv("r-reticulate", required = TRUE)

# Pass pipeline path from R to Python
py_pipeline_path <- path_py_pipeline_src

# Load Python pipeline and patch event extraction for S-format triggers
py_run_string("
import sys
import os
import re

# Clear any previously loaded pipeline modules to avoid conflicts
pipeline_modules = [key for key in list(sys.modules.keys()) if 'pipeline' in key]
for module in pipeline_modules:
    del sys.modules[module]
print(f'Cleared {len(pipeline_modules)} pipeline modules')

# Add local pipeline path
local_path = r.py_pipeline_path
if os.path.exists(local_path):
    if local_path in sys.path:
        sys.path.remove(local_path)
    sys.path.insert(0, local_path)
    print(f'Pipeline path added: {local_path}')
else:
    print(f'Error: Path not found {local_path}')

# Import pipeline
import pipeline
print(f'Pipeline loaded from: {pipeline.__file__}')

# Monkey patch: fixed event extraction for S-format triggers
from pipeline import epoching

def get_events_fixed(raw, triggers):
    '''Fixed version to handle S-format event markers (e.g., S101).'''
    from mne import events_from_annotations
    
    events, event_id = events_from_annotations(raw)
    
    # Extract numeric part from event labels
    def extract_number(key):
        match = re.search(r'\\d+', str(key))
        return int(match.group()) if match else None
    
    # Filter events according to the provided trigger list
    filtered_event_id = {}
    for key, value in event_id.items():
        trigger_num = extract_number(key)
        if trigger_num and trigger_num in triggers:
            filtered_event_id[key] = value
    
    return events, filtered_event_id

# Apply the patch
epoching.get_events = get_events_fixed
print('Applied event extraction fix for S-format triggers')
")

pipeline_mod <- import("pipeline")
```

# 3. Log Preprocessing (Trial-Level and Summary Extraction)

``` {r log-preprocessing}
orig_logs <- list.files(path_raw_log, pattern = "\\.txt$", full.names = TRUE)

cat("Processing", length(orig_logs), "log files...\n")

for (fpath in orig_logs) {
  # 1) Detect file encoding (UTF-16LE vs UTF-8)
  fb  <- file(fpath, "rb")
  bom <- readBin(fb, "raw", n = 2)
  close(fb)
  encoding <- if (length(bom) == 2 && identical(bom, as.raw(c(0xFF, 0xFE)))) "UTF-16LE" else "UTF-8"

  # 2) Read data
  df <- read_delim(
    fpath,
    delim = "\t",
    col_types = cols(),
    show_col_types = FALSE,
    locale = locale(encoding = encoding)
  )

  n <- nrow(df)

  # 3) Extract trial-level data (remove last 3 lines and Block 7)
  df_trials <- df %>% 
    slice(1:(n-3)) %>% 
    filter(block != 7) %>% 
    mutate(emotion = str_extract(stim, "enj|dis|dom|neu|aff"))

  # 4) Extract summary / post-rating data (last 3 lines)
  df_summary <- df %>% slice((n-2):n)

  # 5) Save outputs
  out_name <- paste0(tools::file_path_sans_ext(basename(fpath)), ".csv")
  out_name_summary <- paste0(tools::file_path_sans_ext(basename(fpath)), "_summaryPostRating.csv")
  
  write_csv(df_trials, file.path(path_csv_filtered, out_name))
  write_csv(df_summary, file.path(path_csv_summary, out_name_summary))
}
cat("Log preprocessing complete.\n")
```

# 4. Condition Definitions for Face Phase

``` {r define-conditions}
# ------------------------------------------------------------------------------
# Condition definitions for face-locked analyses
#  - Five facial expressions (enj, dis, dom, neu, aff)
#  - Valid trials: reaction > 0
#    (no RT restriction is applied here, in accordance with the original script)
# ------------------------------------------------------------------------------

face_average_by <- list(
  Face_enj = "emotion=='enj' & reaction>0",
  Face_dis = "emotion=='dis' & reaction>0",
  Face_dom = "emotion=='dom' & reaction>0",
  Face_neu = "emotion=='neu' & reaction>0",
  Face_aff = "emotion=='aff' & reaction>0"
)

# Helper function: copy trials.csv from a source directory to a destination
copy_trials_csv <- function(src_dir, dest_dir, filename = "trials.csv") {
  src <- file.path(src_dir, "trials.csv")
  if (file.exists(src)) {
    file_copy(src, file.path(dest_dir, filename), overwrite = TRUE)
    cat(sprintf(">> Exported to: %s/%s\n", basename(dest_dir), filename))
  } else {
    warning(sprintf("Source file not found: %s", src))
  }
}
```

# 5. ERP Component Extraction (Face Phase, With/Without Baseline Correction)

This section extracts face-locked ERP components: P1, N170, EPN, and LPP_face.
The `baseline` argument is controlled by `baseline_arg` defined in the setup section.

``` {r face-phase}
if (run_face_phase) {

  out_face <- file.path(path_output_root, "face_phase")
  dir.create(out_face, showWarnings = FALSE, recursive = TRUE)

  cat("\n--- Running Face Phase Extraction ---\n")

  res_face <- pipeline_mod$group_pipeline(
    raw_files     = path_raw_eeg,
    log_files     = path_csv_filtered,
    output_dir    = out_face,
    epochs_dir    = file.path(out_face, "epochs"),
    ica_method    = "fastica",
    ica_n_components = 0.99,
    triggers      = c(101:115, 201:215),
    bad_channels  = "auto",
    highpass_freq = 0.05,
    lowpass_freq  = 30.0,
    reject_peak_to_peak = 200.0,
    baseline      = baseline_arg,
    components    = list(
      name = list("P1","N170","EPN","LPP_face"),
      tmin = list(0.080,0.130,0.200,0.500),  
      tmax = list(0.130,0.200,0.350,0.800),  
      roi  = list(
        c("O1","O2","Oz","PO7","PO8"),                               # P1 ROI
        c("TP9","TP10","P7","P8","PO9","PO10","O1","O2"),            # N170 ROI
        c("PO7","PO8","PO9","PO10","TP9","TP10"),                    # EPN ROI
        c("Pz","Cz","C1","C2","CP1","CP2")                           # LPP_face ROI
      )
    ),
    average_by = face_average_by
  )

  # Archive for statistical analysis
  copy_trials_csv(out_face, path_dest_face)
}
```

# 6. ROI-Specific Baseline Extraction (Face Phase LPP)

This section extracts an ROI-specific baseline measure (–200 to 0 ms) for the face-phase LPP component.
Baseline extraction is only performed when no baseline correction has been applied during preprocessing (`use_baseline_correction == FALSE`).

``` {r baseline-face-phase}
if (!use_baseline_correction && run_face_phase) {

  out_bl_face <- file.path(path_output_root, "baseline_Face")
  dir.create(out_bl_face, showWarnings = FALSE, recursive = TRUE)

  cat("\n--- Extracting Baseline for Face Phase (LPP ROI) ---\n")

  pipeline_mod$group_pipeline(
    raw_files     = path_raw_eeg,
    log_files     = path_csv_filtered,
    output_dir    = out_bl_face,
    epochs_dir    = file.path(out_bl_face, "epochs"),
    ica_method    = "fastica",
    ica_n_components = 0.99,
    triggers      = c(101:115, 201:215),  # Face phase triggers
    bad_channels  = "auto",
    highpass_freq = 0.05,
    lowpass_freq  = 30.0,
    baseline      = NULL,   # No correction; direct averaging of -200–0 ms
    reject_peak_to_peak = 200.0,
    components    = list(
      name = list("LPPfacebaseline"),
      tmin = list(-0.2),
      tmax = list(0),
      roi  = list(c("Pz","Cz","C1","C2","CP1","CP2"))  # Same ROI as LPP_face
    ),
    average_by = face_average_by
  )

  copy_trials_csv(out_bl_face, path_dest_baseline_face)
}
```

# 7. Summary of Generated Files

``` {r summary}
cat("\n========================================\n")
cat("         PREPROCESSING COMPLETE         \n")
cat("========================================\n")
cat("Generated Data Files (Face Phase):\n")
cat("1. Face Phase (P1/N170/EPN/LPP): ", file.path(path_dest_face, "trials.csv"), "\n")

cat("\nBaseline Files (ROI-Specific, if extracted):\n")
cat("2. Face LPP Baseline:          ", file.path(path_dest_baseline_face, "trials.csv"), "\n")
cat("========================================\n")
```
