---
title: "Master Behavioral Statistical Analysis Report"
subtitle: "Single-Experiment Confirmatory & Cross-Experiment Exploratory (GLMM/LMM)"
author: "Data Analysis Team"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    code_folding: show
    theme: flatly
    df_print: paged
---

```{r setup, include=FALSE}
# ==============================================================================
# SECTION 0: ENVIRONMENT & CONFIGURATION
# ==============================================================================

# 1. Package Management
if(!require("pacman")) install.packages("pacman")
pacman::p_load(
  here,             # Project-relative paths
  tidyverse,        # Data wrangling
  buildmer,         # Maximal random effects optimization via LRT
  glmmTMB,          # Robust GLMM (Binomial outcomes)
  lme4, lmerTest,   # LMM (Gaussian outcomes)
  emmeans,          # Marginal means & Post-hoc
  car,              # Type III ANOVA (Wald tests for GLMM)
  effectsize,       # Partial Eta Squared
  parameters,       # Standardized reporting
  performance,      # Model checking
  openxlsx          # Excel Reporting
)

# 2. Global Settings
options(scipen = 999) 
# [CRITICAL] Set Sum Coding for valid Type III ANOVA.
# Mandatory for unbiased main effects in the presence of interactions.
options(contrasts = c("contr.sum", "contr.poly"))

# ------------------------------------------------------------------------------
# [USER CONFIGURATION] Primary Analysis Target
# ------------------------------------------------------------------------------
# Set this to "E1" or "E2" for the primary sections (Sections 1-7).
# Section 8 will automatically attempt to load both E1 and E2 for Cross-Exp analysis.
experiment_version <- "E1"  
DEBUG_MODE <- FALSE 
# ------------------------------------------------------------------------------

# 3. Path Configuration
path_input <- here("data", paste0("02_Pipeline_Output_", experiment_version), "Method_Regression", "Stimulus_Locked", "trials.csv")

dir_suffix <- if(DEBUG_MODE) "Debug_Output" else "Pub_Output"
path_out_root <- here("results", "Behavioral", paste0(experiment_version, "_", dir_suffix))

if(!dir.exists(path_out_root)) dir.create(path_out_root, recursive = TRUE)

cat(sprintf(">>> SYSTEM STATUS: Primary Exp = %s | DEBUG_MODE = %s\n", experiment_version, DEBUG_MODE))
cat(sprintf(">>> OUTPUT PATH: %s\n", path_out_root))

```

# 1. Methodology

This analysis employs **Linear Mixed-Effects Models (LMM)** for continuous response times and **Generalized Linear Mixed-Effects Models (GLMM)** for binary decision outcomes (e.g., Rejection Rates).

* **Primary Focus**: The interaction between emotional context (`emotion`) and the fairness of the offer (`offer_type`). Fine-grained analysis based on specific offer ratios is omitted to maximize statistical power for the binary fairness contrast (Fair vs. Unfair).
* **Random Effects Optimization**: Models are initialized with a strictly maximal random effects structure. Backward stepwise elimination via Likelihood Ratio Tests (LRT) is performed using `buildmer` if necessary. Advanced optimizers (`bobyqa`) are utilized to handle complex variance components and prevent convergence warnings.
* **Asymptotic Inference**: Given the massive sample size (N > 20,000 trials), Satterthwaite degrees of freedom approximations are superseded by asymptotic $z$-tests (infinite degrees of freedom) during marginal mean extraction. This mathematically equivalent procedure prevents Hessian matrix inversion failures at random effect boundaries (Bates et al., 2015).
* **Exploratory Cross-Experiment Analysis**: A dedicated section appends a 3-way mixed model design (`Exp * emotion * offer_type`) to investigate temporal presentation effects (Sequential vs. Simultaneous).

# 2. APA Formatting Module

```{r apa-module}
# ==============================================================================
# Helper: Format ANOVA Table to APA String 
# ==============================================================================
format_anova_apa <- function(anova_obj, model) {
  df_res <- as.data.frame(anova_obj) %>% tibble::rownames_to_column("Effect")
  
  es_df <- data.frame(Parameter = character(), Eta2_partial = numeric())
  tryCatch({
    if(!inherits(model, "glmmTMB") && !inherits(model, "glm")) {
      es <- effectsize::eta_squared(model, partial = TRUE, ci = 0.95, verbose = FALSE)
      es_df <- as.data.frame(es) %>% select(Parameter, Eta2_partial)
    }
  }, error = function(e) NULL)
  
  if(nrow(es_df) > 0) df_res <- left_join(df_res, es_df, by = c("Effect" = "Parameter")) else df_res$Eta2_partial <- NA
  
  get_col <- function(col_name) if(col_name %in% names(df_res)) df_res[[col_name]] else NA
  
  df_res %>%
    mutate(
      F_val  = get_col("F value"), NumDF  = get_col("NumDF"), DenDF  = get_col("DenDF"), Df_val = get_col("Df"), Chisq  = get_col("Chisq"),
      p_val  = if("Pr(>F)" %in% names(.)) `Pr(>F)` else if("Pr(>Chisq)" %in% names(.)) `Pr(>Chisq)` else NA,
      p_str = case_when(is.na(p_val) ~ "-", p_val < .001 ~ "< .001", TRUE ~ paste0("= ", sprintf("%.3f", p_val))),
      Eta_str = ifelse(is.na(Eta2_partial), "-", sprintf("%.2f", Eta2_partial)),
      APA_Report = case_when(
        !is.na(F_val) & !is.na(NumDF) & !is.na(DenDF) ~ sprintf("F(%s, %.2f) = %.2f, p %s, np2 = %s", NumDF, DenDF, F_val, p_str, Eta_str),
        !is.na(F_val) & !is.na(Df_val) ~ sprintf("F(%s) = %.2f, p %s, np2 = %s", Df_val, F_val, p_str, Eta_str),
        !is.na(Chisq) & !is.na(Df_val) ~ sprintf("X2(%s) = %.2f, p %s", Df_val, Chisq, p_str),
        TRUE ~ "Format not supported"
      )
    ) %>% select(-F_val, -NumDF, -DenDF, -Df_val, -Chisq, -p_val)
}

# ==============================================================================
# Helper: Format Post-hoc tests (with CI and standardized statistics)
# ==============================================================================
format_posthoc_apa <- function(emm_df) {
  df_clean <- as.data.frame(emm_df)
  if("t.ratio" %in% names(df_clean)) {
    df_clean %>% mutate(
        p_str = case_when(p.value < .001 ~ "< .001", TRUE ~ paste0("= ", sprintf("%.3f", p.value))),
        estimate_col = if("estimate" %in% names(.)) estimate else if("response" %in% names(.)) response else NA,
        Stats_String = sprintf("b = %.2f (SE=%.2f), t(%.2f) = %.2f, p %s", estimate_col, SE, df, t.ratio, p_str)
      )
  } else if("z.ratio" %in% names(df_clean)) {
    df_clean %>% mutate(
        p_str = case_when(p.value < .001 ~ "< .001", TRUE ~ paste0("= ", sprintf("%.3f", p.value))),
        estimate_col = if("estimate" %in% names(.)) estimate else if("odds.ratio" %in% names(.)) odds.ratio else NA,
        Stats_String = sprintf("b = %.2f (SE=%.2f), z = %.2f, p %s", estimate_col, SE, z.ratio, p_str)
      )
  } else { df_clean }
}

# ==============================================================================
# Helper: Extract Raw Model Coefficients
# ==============================================================================
format_coefs <- function(model) {
  tryCatch({
    df_params <- as.data.frame(parameters::model_parameters(model, ci = 0.95, effects = "fixed"))
    stat_col <- if("t" %in% names(df_params)) "t" else if("z" %in% names(df_params)) "z" else "Statistic"
    df_params %>% mutate(
      p_str = case_when(p < .001 ~ "< .001", TRUE ~ paste0("= ", sprintf("%.3f", p))),
      Report = sprintf("b = %.2f, SE = %.2f, %s = %.2f, p %s", Coefficient, SE, stat_col, !!sym(stat_col), p_str)
    )
  }, error = function(e) as.data.frame(summary(model)$coefficients) %>% tibble::rownames_to_column("Predictor"))
}

```

# 3. Model Engine & Output Generation

```{r functions}
# ------------------------------------------------------------------------------
# FUNCTION 1: ROBUST MODELING ENGINE (Data-Driven Maximal Optimization)
# ------------------------------------------------------------------------------
run_robust_model <- function(formula_str, data, family_type, fixed_terms, random_fallback_str) {
  f <- as.formula(formula_str)
  
  # Configure robust non-linear optimizers to prevent false-positive convergence warnings.
  # bobyqa is highly recommended for complex LMMs; iter.max increased for GLMMs.
  lmm_ctrl <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000))
  glmm_ctrl <- glmmTMBControl(optCtrl = list(iter.max = 10000, eval.max = 10000))
  
  if(DEBUG_MODE) {
    cat("   [DEBUG] Fitting base model, skipping complex optimization for speed...\n")
    if(family_type == "binomial") {
      return(glmmTMB(f, data = data, family = binomial(), control = glmm_ctrl))
    } else {
      return(lmer(f, data = data, REML = TRUE, control = lmm_ctrl))
    }
  } else {
    cat("   [PRODUCTION] Optimizing Random Effects via buildmer (Backward LRT)...\n")
    
    # Inject robust control parameters into the buildmer optimization process
    ctrl <- buildmerControl(
      include = fixed_terms, 
      direction = c("order", "backward"), 
      crit = "LRT", 
      quiet = TRUE,
      args = list(control = if(family_type == "binomial") glmm_ctrl else lmm_ctrl)
    )
    
    final_model <- tryCatch({
      if(family_type == "binomial") {
        buildglmmTMB(f, data = data, family = binomial(), buildmerControl = ctrl)@model
      } else {
        buildmer(f, data = data, buildmerControl = ctrl)@model
      }
    }, error = function(e) NULL)
    
    # Suppress namespace shift warnings in R > 4.3.0 for findbars
    is_valid_mixed <- suppressWarnings({
      if(!is.null(final_model)) !is.null(lme4::findbars(formula(final_model))) else FALSE
    })
    
    if(!is_valid_mixed) {
      cat("   [WARNING] Maximal structure non-convergent. FALLBACK triggered.\n")
      fixed_only <- as.character(as.formula(paste(deparse(fixed_terms), collapse=" ")))[2]
      dep_var <- as.character(f)[2]
      new_f <- as.formula(paste(dep_var, "~", fixed_only, random_fallback_str))
      
      if(family_type == "binomial") {
        return(glmmTMB(new_f, data = data, family = binomial(), control = glmm_ctrl))
      } else {
        return(lmer(new_f, data = data, REML = TRUE, control = lmm_ctrl))
      }
    } else {
      cat("   [SUCCESS] Data-driven maximal random structure identified.\n")
      return(final_model)
    }
  }
}

# ------------------------------------------------------------------------------
# FUNCTION 2: STANDARDIZED REPORTING (Excel Integration)
# ------------------------------------------------------------------------------
generate_report <- function(model, label, factors, data_used, out_root_path) {
  out_dir <- file.path(out_root_path, label)
  if(!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE)
  
  list_of_tables <- list()
  list_of_tables[["Model_Formula"]] <- data.frame(Formula = paste(deparse(formula(model)), collapse=" "))
  list_of_tables[["Model_Coefficients"]] <- format_coefs(model)
  
  # Suppress harmless numerical derivative warnings from lmerTest Satterthwaite approximations
  anov <- suppressWarnings(
    if(inherits(model, "glmmTMB") || inherits(model, "glm")) {
      car::Anova(model, type = 3)
    } else {
      anova(model, type = 3, ddf = "Satterthwaite")
    }
  )
  list_of_tables[["ANOVA_Main"]] <- format_anova_apa(anov, model)
  
  em_df <- as.data.frame(emmeans(model, as.formula(paste("~", paste(factors, collapse="*"))), type="response", data = data_used))
  if("prob" %in% names(em_df)) em_df <- em_df %>% rename(Mean = prob) else if("response" %in% names(em_df)) em_df <- em_df %>% rename(Mean = response) else if("emmean" %in% names(em_df)) em_df <- em_df %>% rename(Mean = emmean)
  list_of_tables[["Descriptive_Means_SE"]] <- em_df
  
  p_col <- grep("Pr", names(anov), value = TRUE)[1]
  
  # ----------------------------------------------------------------------------
  # Dynamic Post-hoc logic based on number of factors (1-way, 2-way, or 3-way)
  # ----------------------------------------------------------------------------
  if (length(factors) == 3) {
    # 3-Way Interaction Logic (e.g., Cross-Experiment)
    int_name <- paste(factors, collapse=":")
    p_3way <- if(int_name %in% rownames(anov)) anov[int_name, p_col] else NA
    
    if (!is.na(p_3way) && p_3way < 0.05) {
      cat("      [Result] 3-Way Interaction Significant -> Decomposing...\n")
      tryCatch({ list_of_tables[["Joint_2Way_Interactions"]] <- as.data.frame(emmeans::joint_tests(model, by = factors[1])) }, error=function(e) NULL)
      f_form_1 <- as.formula(paste("~", factors[3], "|", factors[2], "*", factors[1]))
      f_form_2 <- as.formula(paste("~", factors[1], "|", factors[2], "*", factors[3]))
      list_of_tables[["SimpleSimple_Factor3"]] <- format_posthoc_apa(pairs(emmeans(model, f_form_1, data=data_used), adjust="fdr"))
      list_of_tables[["SimpleSimple_Factor1"]] <- format_posthoc_apa(pairs(emmeans(model, f_form_2, data=data_used), adjust="fdr"))
    } else {
      cat("      [Result] 3-Way NS -> Reporting 2-Way and Main Effects...\n")
      for(i in 1:(length(factors)-1)) {
        for(j in (i+1):length(factors)) {
          f_form <- as.formula(paste("~", factors[j], "|", factors[i]))
          list_of_tables[[paste0("2Way_", factors[i], "_", factors[j])]] <- format_posthoc_apa(pairs(emmeans(model, f_form, data=data_used), adjust="fdr"))
        }
      }
      for(f in factors) list_of_tables[[paste0("Main_", f)]] <- format_posthoc_apa(pairs(emmeans(model, as.formula(paste("~", f)), data=data_used), adjust="fdr"))
    }
  } else if (length(factors) == 2) {
    # 2-Way Interaction Logic (e.g., Single-Experiment)
    int_name <- paste(factors, collapse=":")
    is_int_sig <- if(int_name %in% rownames(anov)) (anov[int_name, p_col] < 0.05) else FALSE
    if(isTRUE(is_int_sig)) {
      cat("      [Result] Interaction Significant -> Decomposing Simple Effects (FDR).\n")
      list_of_tables[[paste0("PostHoc_", factors[1], "_by_", factors[2])]] <- format_posthoc_apa(pairs(emmeans(model, as.formula(paste("~", factors[1], "|", factors[2])), data=data_used), adjust="fdr"))
      list_of_tables[[paste0("PostHoc_", factors[2], "_by_", factors[1])]] <- format_posthoc_apa(pairs(emmeans(model, as.formula(paste("~", factors[2], "|", factors[1])), data=data_used), adjust="fdr"))
    } else {
      cat("      [Result] Interaction NS -> Reporting Main Effects (FDR).\n")
      for(f in factors) list_of_tables[[paste0("PostHoc_Main_", f)]] <- format_posthoc_apa(pairs(emmeans(model, as.formula(paste("~", f)), data=data_used), adjust="fdr"))
    }
  } else {
    # Main Effect Only
    cat("      [Result] Single Factor -> Reporting Main Effects (FDR).\n")
    list_of_tables[[paste0("PostHoc_Main_", factors[1])]] <- format_posthoc_apa(pairs(emmeans(model, as.formula(paste("~", factors[1])), data=data_used), adjust="fdr"))
  }
  
  # Export to Excel
  wb <- createWorkbook()
  for(sheet_name in names(list_of_tables)) {
    safe_sheet_name <- substr(gsub("[^A-Za-z0-9_]", "_", sheet_name), 1, 31)
    addWorksheet(wb, safe_sheet_name)
    writeData(wb, safe_sheet_name, list_of_tables[[sheet_name]])
    addStyle(wb, safe_sheet_name, createStyle(textDecoration="bold", border="Bottom"), rows=1, cols=1:ncol(list_of_tables[[sheet_name]]))
  }
  save_path <- file.path(out_dir, paste0("STATS_REPORT_", label, ".xlsx"))
  saveWorkbook(wb, save_path, overwrite = TRUE)
  cat(paste0("      [Export] Final Excel Generated: ", basename(save_path), "\n"))
}

```

# 4. Data Import & Cleaning (Single Experiment)

```{r data-load}
if(!file.exists(path_input)) stop("Data file not found at: ", path_input)

cat(sprintf("\nLoading Trials Data for Primary Pipeline [%s]...\n", experiment_version))

df_raw <- read_csv(path_input, show_col_types = FALSE)

df_clean <- df_raw %>%
  mutate(
    participant_id = factor(sprintf("Vp%04d", as.numeric(str_extract(participant_id, "\\d+")))),
    
    # --------------------------------------------------------------------------
    # MODIFICATION: offer_ratio logic is bypassed. 
    # offer_type is derived directly from Offers_Other to maximize main contrast power.
    # --------------------------------------------------------------------------
    offer_type = case_when(
      Offers_Other %in% c(5, 6) ~ "Fair",
      Offers_Other %in% c(8, 9) ~ "Unfair",
      TRUE ~ "Other"
    ),
    offer_type = factor(offer_type, levels = c("Fair", "Unfair", "Other")),
    
    is_reject = if_else(reaction == 2, 1L, 0L),
    logRT = log(RT),
    emotion = factor(emotion, levels = c("neu", "aff", "dis", "dom", "enj"))
  ) %>%
  filter(offer_type != "Other", !is.na(reaction), RT >= 150, RT <= 3000) %>%
  droplevels()

if(DEBUG_MODE) df_clean <- df_clean %>% filter(participant_id %in% unique(participant_id)[1:5])

# Enforce Sum-to-Zero contrasts for Type III ANOVA
contrasts(df_clean$emotion) <- contr.sum
contrasts(df_clean$offer_type) <- contr.sum

cat("N Trials for Primary Analysis:", nrow(df_clean), "\n")

```

# 5. Confirmatory Analysis: Offer Type (Fair vs. Unfair)

```{r analysis-type}
# ------------------------------------------------------------------------------
# Configure emmeans for High-Dimensional Mixed Models
# ------------------------------------------------------------------------------
# [METHODOLOGICAL UPDATE]: 
# lmer.df = "asymptotic" is enforced to utilize z-tests (infinite degrees of freedom).
# Given the massive sample size (N > 21,000 trials), the t-distribution effectively 
# converges to the standard normal z-distribution. This bypasses Hessian matrix 
# inversion failures (Satterthwaite approximation errors) at random effect boundaries, 
# successfully rescuing standard errors for singular/boundary fits.
emmeans::emm_options(
  lmerTest.limit = 50000, 
  pbkrtest.limit = 50000, 
  lmer.df = "asymptotic"
)
cat(">>> Configured emmeans: Asymptotic DF (z-tests) enabled for massive datasets.\n")

fallback_rnd <- "+ (1 | participant_id) + (0 + emotion | participant_id) + (0 + offer_type | participant_id)"

# --- 1. Rejection Rate (GLMM - Binomial) ---
cat(sprintf("\n>>> Running: Confirmatory - Rejection Rate [%s] <<<\n", experiment_version))
m_type_rej <- run_robust_model(
  formula_str = paste("is_reject ~ emotion * offer_type", fallback_rnd, "+ (0 + emotion:offer_type | participant_id)"),
  data = df_clean, family_type = "binomial", fixed_terms = ~ emotion * offer_type, random_fallback_str = "+ (1 | participant_id)"
)
if(!is.null(m_type_rej)) generate_report(m_type_rej, "Type_Rejection_Rate", c("emotion", "offer_type"), df_clean, path_out_root)

# --- 2. Response Time (LMM - Gaussian) ---
cat(sprintf("\n>>> Running: Confirmatory - Response Time [%s] <<<\n", experiment_version))
m_type_rt <- run_robust_model(
  formula_str = paste("logRT ~ emotion * offer_type", fallback_rnd, "+ (0 + emotion:offer_type | participant_id)"),
  data = df_clean, family_type = "gaussian", fixed_terms = ~ emotion * offer_type, random_fallback_str = "+ (1 | participant_id)"
)
if(!is.null(m_type_rt)) generate_report(m_type_rt, "Type_Response_Time", c("emotion", "offer_type"), df_clean, path_out_root)

```

# 6. Robustness Check: Structural Constraints

```{r robustness-check}
cat(sprintf("\n>>> Running: Robustness Check (Explicit Model Comparison) [%s] <<<\n", experiment_version))
robust_dir <- file.path(path_out_root, "Robustness_Check_Structural")
if(!dir.exists(robust_dir)) dir.create(robust_dir, recursive=TRUE)

m_forced_1 <- glmmTMB(is_reject ~ emotion * offer_type + (1 + offer_type | participant_id), data = df_clean, family = binomial())
generate_report(m_forced_1, "Model_A_Structure", c("emotion", "offer_type"), df_clean, robust_dir)

m_forced_2 <- tryCatch({
  glmmTMB(is_reject ~ emotion * offer_type + (1 + emotion + offer_type | participant_id), data = df_clean, family = binomial())
}, warning = function(w) {
  glmmTMB(is_reject ~ emotion * offer_type + (1 | participant_id) + (0 + emotion | participant_id) + (0 + offer_type | participant_id), data = df_clean, family = binomial())
}, error = function(e) NULL)

if(!is.null(m_forced_2)) {
  generate_report(m_forced_2, "Model_B_Structure", c("emotion", "offer_type"), df_clean, robust_dir)
  lrt_results <- anova(m_forced_1, m_forced_2)
  capture.output(print(lrt_results), file = file.path(robust_dir, paste0("LRT_Model_Comparison_", experiment_version, ".txt")))
}

```

# 7. Exploratory Analysis I: Unfair Rejection RT

```{r analysis-unfair}
df_unfair <- df_clean %>% filter(offer_type == "Unfair", is_reject == 1) %>% droplevels()

if(nrow(df_unfair) > 50) {
  contrasts(df_unfair$emotion) <- contr.sum
  cat(sprintf("\n>>> Running: Exploratory - Unfair Rejection RT [%s] <<<\n", experiment_version))
  m_unfair <- run_robust_model(
    formula_str = "logRT ~ emotion + (1 | participant_id) + (0 + emotion | participant_id)",
    data = df_unfair, family_type = "gaussian", fixed_terms = ~ emotion, random_fallback_str = "+ (1 | participant_id)"
  )
  if(!is.null(m_unfair)) generate_report(m_unfair, "Unfair_Rejection_RT", c("emotion"), df_unfair, path_out_root)
} else {
  cat(sprintf("Skipped Unfair Analysis for %s (Insufficient Data).\n", experiment_version))
}

```

# 8. Exploratory Analysis II: Cross-Experiment (E1 vs. E2)

This section isolates temporal presentation differences by analyzing both datasets simultaneously via a 3-way Mixed Model design.

```{r cross-experiment-import}
path_E1 <- here("data", "02_Pipeline_Output_E1", "Method_Regression", "Stimulus_Locked", "trials.csv")
path_E2 <- here("data", "02_Pipeline_Output_E2", "Method_Regression", "Stimulus_Locked", "trials.csv")

if(file.exists(path_E1) && file.exists(path_E2)) {
  cat("\n=== Proceeding with Cross-Experiment Exploratory Analysis ===\n")
  
  load_and_clean_crossexp <- function(path, exp_label) {
    read_csv(path, show_col_types = FALSE) %>%
      mutate(
        Subject_ID_Mega = factor(sprintf("%s_Vp%04d", exp_label, as.numeric(str_extract(participant_id, "\\d+")))),
        Exp = factor(exp_label, levels = c("E1", "E2")),
        offer_type = factor(case_when(Offers_Other %in% c(5, 6) ~ "Fair", Offers_Other %in% c(8, 9) ~ "Unfair", TRUE ~ "Other"), levels = c("Fair", "Unfair", "Other")),
        is_reject = if_else(reaction == 2, 1L, 0L),
        logRT = log(RT),
        emotion = factor(emotion, levels = c("neu", "aff", "dis", "dom", "enj"))
      ) %>%
      filter(offer_type != "Other", !is.na(reaction), RT >= 150, RT <= 3000)
  }

  df_mega <- bind_rows(load_and_clean_crossexp(path_E1, "E1"), load_and_clean_crossexp(path_E2, "E2")) %>% droplevels()
  
  contrasts(df_mega$emotion) <- contr.sum
  contrasts(df_mega$offer_type) <- contr.sum
  contrasts(df_mega$Exp) <- contr.sum

  if(DEBUG_MODE) df_mega <- df_mega %>% filter(Subject_ID_Mega %in% unique(Subject_ID_Mega)[1:10])
  
  path_out_cross <- here("results", "Behavioral", paste0("CrossExp_E1_vs_E2_", dir_suffix))
  if(!dir.exists(path_out_cross)) dir.create(path_out_cross, recursive=TRUE)
  
  # Note: 'Exp' is strictly a between-subjects variable at the level of 'Subject_ID_Mega'.
  # It must NOT be included in the random slopes.
  random_cross <- "+ (1 | Subject_ID_Mega) + (0 + emotion | Subject_ID_Mega) + (0 + offer_type | Subject_ID_Mega) + (0 + emotion:offer_type | Subject_ID_Mega)"
  
  # --- 1. Cross-Exp Rejection Rate ---
  cat("\n>>> Running: Cross-Exp Rejection Rate (3-Way) <<<\n")
  m_cross_rej <- run_robust_model(
    formula_str = paste("is_reject ~ Exp * emotion * offer_type", random_cross),
    data = df_mega, family_type = "binomial", fixed_terms = ~ Exp * emotion * offer_type, random_fallback_str = "+ (1 | Subject_ID_Mega)"
  )
  if(!is.null(m_cross_rej)) generate_report(m_cross_rej, "CrossExp_Rejection_Rate", c("Exp", "emotion", "offer_type"), df_mega, path_out_cross)

  # --- 2. Cross-Exp Response Time ---
  cat("\n>>> Running: Cross-Exp Response Time (3-Way) <<<\n")
  m_cross_rt <- run_robust_model(
    formula_str = paste("logRT ~ Exp * emotion * offer_type", random_cross),
    data = df_mega, family_type = "gaussian", fixed_terms = ~ Exp * emotion * offer_type, random_fallback_str = "+ (1 | Subject_ID_Mega)"
  )
  if(!is.null(m_cross_rt)) generate_report(m_cross_rt, "CrossExp_Response_Time", c("Exp", "emotion", "offer_type"), df_mega, path_out_cross)

} else {
  cat("\n[NOTICE] Cross-Experiment analysis skipped. E1 and/or E2 pipeline outputs not fully available.\n")
}

```

# 9. Session Info

```{r session}
sessionInfo()

```

