---
title: "UG Behavioral Statistical Analysis Report"
subtitle: "Publication-Quality Modeling (GLMM/LMM) with Data-Driven Maximal Random Structure"
author: "Data Analysis Team"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    code_folding: show
    theme: flatly
    df_print: paged
---

```{r setup, include=FALSE}
# ==============================================================================
# SECTION 0: ENVIRONMENT & CONFIGURATION
# ==============================================================================

# 1. Package Management
if(!require("pacman")) install.packages("pacman")
pacman::p_load(
  here,             # Project-relative paths
  tidyverse,        # Data wrangling
  buildmer,         # Maximal random effects optimization via LRT
  glmmTMB,          # Robust GLMM (Binomial outcomes)
  lme4, lmerTest,   # LMM (Gaussian outcomes)
  emmeans,          # Marginal means & Post-hoc
  car,              # Type III ANOVA (Wald tests for GLMM)
  effectsize,       # Partial Eta Squared
  parameters,       # Standardized reporting
  performance,      # Model checking
  openxlsx          # Excel Reporting
)

# 2. Global Settings
options(scipen = 999) 
# [CRITICAL] Set Sum Coding for valid Type III ANOVA
# Mandatory for unbiased main effects in the presence of interactions.
options(contrasts = c("contr.sum", "contr.poly"))

# ------------------------------------------------------------------------------
# [USER CONFIGURATION] Global Settings & Analysis Targets
# ------------------------------------------------------------------------------
# Set this to "E1" or "E2" depending on which project folder you are running.
# This ensures output reports and folders are cleanly isolated.
experiment_version <- "E2"  
DEBUG_MODE <- FALSE 
# ------------------------------------------------------------------------------

# 3. Path Configuration
# [MATCHED WITH EEG PIPELINE]: Reads exactly from where the EEG script dumps the trials.
path_input <- here("data", "02_Pipeline_Output", "Method_Regression", "Stimulus_Locked", "trials.csv")

# [UPGRADED]: Isolates output reporting by Experiment Version to prevent overwrite.
dir_suffix <- if(DEBUG_MODE) "Debug_Output_Final" else "Pub_Output_Final"
path_out_root <- here("results", "Behavioral", paste0(experiment_version, "_", dir_suffix))

if(!dir.exists(path_out_root)) dir.create(path_out_root, recursive = TRUE)

cat(sprintf(">>> SYSTEM STATUS: Experiment = %s | DEBUG_MODE = %s\n", experiment_version, DEBUG_MODE))
cat(sprintf(">>> INPUT PATH DETECTED: %s\n", path_input))
cat(sprintf(">>> OUTPUT PATH: %s\n", path_out_root))



```

# 1. Methodology

This analysis employs **Linear Mixed-Effects Models (LMM)** for continuous response times and **Generalized Linear Mixed-Effects Models (GLMM)** for binary decision outcomes (e.g., Rejection Rates). The analysis is dynamically configured for **`r experiment_version`**.

* **Random Effects Optimization**: To balance Type I error control and statistical power, we follow Matuschek et al. (2017) and Barr et al. (2013). Models are initialized with a strictly maximal random effects structure utilizing Zero-Correlation Parameterization (ZCP) to prevent singular fits in complex factorial designs. The `buildmer` package is utilized to perform backward stepwise elimination via Likelihood Ratio Tests (LRT). Nonsignificant random slopes and covariance parameters are sequentially removed until a maximal-justifiable (parsimonious) and convergent structure is achieved. Fixed effects are strictly protected.
* **Inferential Statistics**: For LMMs, we report Type III ANOVA $F$-statistics with Satterthwaite's approximation for degrees of freedom. For binomial GLMMs, we report Type III Wald $\chi^2$ statistics (infinite denominator degrees of freedom).
* **Post-hoc Analysis**: Simple and main effects are adjusted using the False Discovery Rate (FDR) procedure. For high-dimensional exploratory models, asymptotic approximations ($z$-tests) are employed to prevent computational singularity.

# 2. APA Formatting Module

```{r apa-module}
# ==============================================================================
# Helper: Format ANOVA Table to APA String (Supports LMM & GLMM)
# ==============================================================================
format_anova_apa <- function(anova_obj, model) {
  df_res <- as.data.frame(anova_obj) %>% tibble::rownames_to_column("Effect")
  
  # Calculate Partial Eta Squared (Primary for LMMs, NA for GLMMs)
  es_df <- data.frame(Parameter = character(), Eta2_partial = numeric())
  tryCatch({
    if(!inherits(model, "glmmTMB") && !inherits(model, "glm")) {
      es <- effectsize::eta_squared(model, partial = TRUE, ci = 0.95, verbose = FALSE)
      es_df <- as.data.frame(es) %>% select(Parameter, Eta2_partial)
    }
  }, error = function(e) NULL)
  
  if(nrow(es_df) > 0) {
    df_res <- left_join(df_res, es_df, by = c("Effect" = "Parameter"))
  } else {
    df_res$Eta2_partial <- NA
  }
  
  get_col <- function(col_name) if(col_name %in% names(df_res)) df_res[[col_name]] else NA
  
  df_res <- df_res %>%
    mutate(
      F_val  = get_col("F value"),
      NumDF  = get_col("NumDF"),
      DenDF  = get_col("DenDF"),
      Df_val = get_col("Df"),
      Chisq  = get_col("Chisq"),
      p_val  = if("Pr(>F)" %in% names(.)) `Pr(>F)` else if("Pr(>Chisq)" %in% names(.)) `Pr(>Chisq)` else NA,
      
      p_str = case_when(
        is.na(p_val) ~ "-",
        p_val < .001 ~ "< .001",
        TRUE ~ paste0("= ", sprintf("%.3f", p_val))
      ),
      Eta_str = ifelse(is.na(Eta2_partial), "-", sprintf("%.2f", Eta2_partial))
    )
    
  df_res %>%
    mutate(
      APA_Report = case_when(
        !is.na(F_val) & !is.na(NumDF) & !is.na(DenDF) ~ 
          sprintf("F(%s, %.2f) = %.2f, p %s, np2 = %s", NumDF, DenDF, F_val, p_str, Eta_str),
        !is.na(F_val) & !is.na(Df_val) ~ 
          sprintf("F(%s) = %.2f, p %s, np2 = %s", Df_val, F_val, p_str, Eta_str),
        !is.na(Chisq) & !is.na(Df_val) ~ 
          sprintf("X2(%s) = %.2f, p %s", Df_val, Chisq, p_str),
        TRUE ~ "Format not supported"
      )
    ) %>%
    select(-F_val, -NumDF, -DenDF, -Df_val, -Chisq, -p_val)
}

# ==============================================================================
# Helper: Format Post-hoc tests (with CI)
# ==============================================================================
format_posthoc_apa <- function(emm_df) {
  df_clean <- as.data.frame(emm_df)
  
  if("t.ratio" %in% names(df_clean)) {
    # LMM Output Formatting (Satterthwaite DF)
    df_clean <- df_clean %>%
      mutate(
        p_str = case_when(p.value < .001 ~ "< .001", TRUE ~ paste0("= ", sprintf("%.3f", p.value))),
        t_str = sprintf("%.2f", t.ratio),
        df_str = sprintf("%.2f", df),
        estimate_col = if("estimate" %in% names(.)) estimate else if("response" %in% names(.)) response else NA,
        estimate_str = sprintf("%.2f", estimate_col),
        se_str = sprintf("%.2f", SE),
        Stats_String = sprintf("b = %s (SE=%s), t(%s) = %s, p %s", estimate_str, se_str, df_str, t_str, p_str)
      )
  } else if("z.ratio" %in% names(df_clean)) {
    # GLMM Output Formatting (Asymptotic/Infinite DF)
    df_clean <- df_clean %>%
      mutate(
        p_str = case_when(p.value < .001 ~ "< .001", TRUE ~ paste0("= ", sprintf("%.3f", p.value))),
        z_str = sprintf("%.2f", z.ratio),
        estimate_col = if("estimate" %in% names(.)) estimate else if("odds.ratio" %in% names(.)) odds.ratio else NA,
        estimate_str = sprintf("%.2f", estimate_col),
        se_str = sprintf("%.2f", SE),
        Stats_String = sprintf("b = %s (SE=%s), z = %s, p %s", estimate_str, se_str, z_str, p_str)
      )
  }
  return(df_clean)
}

# ==============================================================================
# Helper: Format Raw Coefficients 
# ==============================================================================
format_coefs <- function(model) {
  tryCatch({
    params <- parameters::model_parameters(model, ci = 0.95, effects = "fixed")
    df_params <- as.data.frame(params)
    
    stat_col <- if("t" %in% names(df_params)) "t" else if("z" %in% names(df_params)) "z" else "Statistic"
    
    df_params %>% mutate(
      p_str = case_when(p < .001 ~ "< .001", TRUE ~ paste0("= ", sprintf("%.3f", p))),
      Report = sprintf("b = %.2f, SE = %.2f, %s = %.2f, p %s", Coefficient, SE, stat_col, !!sym(stat_col), p_str)
    )
  }, error = function(e) {
    coef_df <- summary(model)$coefficients
    if(is.list(coef_df) && "cond" %in% names(coef_df)) coef_df <- coef_df$cond
    as.data.frame(coef_df) %>% tibble::rownames_to_column("Predictor")
  })
}


```

# 3. Model Engine & Output Generation

```{r functions}
# ------------------------------------------------------------------------------
# FUNCTION 1: ROBUST MODELING ENGINE (Data-Driven Maximal Optimization)
# ------------------------------------------------------------------------------
run_robust_model <- function(formula_str, data, family_type, fixed_terms) {
  
  f <- as.formula(formula_str)
  
  if(DEBUG_MODE) {
    cat("   [DEBUG] Fitting base model, skipping complex optimization for speed...\n")
    suppressWarnings({
      if(family_type == "binomial") {
        return(glmmTMB(f, data = data, family = binomial()))
      } else {
        return(lmer(f, data = data, REML = TRUE))
      }
    })
  } else {
    cat("   [PRODUCTION] Optimizing Random Effects via buildmer (Backward LRT)...\n")
    
    # Strictly protect fixed effects while allowing backward elimination of random slopes
    ctrl <- buildmerControl(
      include = fixed_terms, 
      direction = c("order", "backward"),
      crit = "LRT",
      quiet = TRUE
    )
    
    final_model <- tryCatch({
      if(family_type == "binomial") {
        bm <- buildglmmTMB(f, data = data, family = binomial(), buildmerControl = ctrl)
        bm@model
      } else {
        bm <- buildmer(f, data = data, buildmerControl = ctrl)
        bm@model
      }
    }, error = function(e) {
      cat("   [ERROR] Optimization failed critically. Fallback triggered.\n")
      return(NULL)
    })
    
    if(!is.null(final_model)) {
      is_valid_mixed <- !is.null(lme4::findbars(formula(final_model)))
    } else {
      is_valid_mixed <- FALSE
    }
    
    if(is.null(final_model) || !is_valid_mixed) {
      cat("   [WARNING] Maximal structure non-convergent. FALLBACK: Random Intercept Only.\n")
      
      fixed_only <- as.formula(paste(deparse(fixed_terms), collapse=" "))
      dep_var <- as.character(f)[2]
      new_f_str <- paste(dep_var, "~", as.character(fixed_only)[2], "+ (1 | participant_id)")
      new_f <- as.formula(new_f_str)
      
      if(family_type == "binomial") {
        return(glmmTMB(new_f, data = data, family = binomial()))
      } else {
        return(lmer(new_f, data = data, REML = TRUE))
      }
    } else {
      cat("   [SUCCESS] Data-driven maximal random structure identified.\n")
      cat("   [FINAL FORMULA]:", paste(deparse(formula(final_model)), collapse=" "), "\n")
      return(final_model)
    }
  }
}

# ------------------------------------------------------------------------------
# FUNCTION 2: STANDARDIZED REPORTING (Excel Integration)
# ------------------------------------------------------------------------------
generate_report <- function(model, label, factors, data_used) {
  
  out_dir <- file.path(path_out_root, label)
  if(!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE)
  
  cat(paste0("   -> Generating Reports in: ", label, "\n"))
  list_of_tables <- list()
  
  list_of_tables[["Model_Formula"]] <- data.frame(Formula = paste(deparse(formula(model)), collapse=" "))
  list_of_tables[["Model_Coefficients"]] <- format_coefs(model)
  
  # Type III ANOVA Extraction
  # Note: glmmTMB models utilize Wald Chi-Square tests via car::Anova.
  # Lmer models utilize Satterthwaite approximations.
  if(inherits(model, "glmmTMB") || inherits(model, "glm")) {
    anov <- car::Anova(model, type = 3)
  } else {
    anov <- anova(model, type = 3, ddf = "Satterthwaite")
  }
  list_of_tables[["ANOVA_Main"]] <- format_anova_apa(anov, model)
  
  em <- emmeans(model, as.formula(paste("~", paste(factors, collapse="*"))), type="response", data = data_used)
  em_df <- as.data.frame(em)
  
  if("prob" %in% names(em_df)) em_df <- em_df %>% rename(Mean = prob)
  else if("response" %in% names(em_df)) em_df <- em_df %>% rename(Mean = response)
  else if("emmean" %in% names(em_df)) em_df <- em_df %>% rename(Mean = emmean)
  list_of_tables[["Descriptive_Means_SE"]] <- em_df
  
  p_col <- grep("Pr", names(anov), value = TRUE)[1]
  int_rows <- grep(":", rownames(anov))
  is_int_sig <- any(anov[int_rows, p_col] < 0.05, na.rm = TRUE)
  
  if(isTRUE(is_int_sig) && length(factors) >= 2) {
    cat("      [Result] Interaction Significant -> Decomposing Simple Effects (FDR).\n")
    f1 <- factors[1]; f2 <- factors[2]
    
    res1 <- pairs(emmeans(model, as.formula(paste("~", f1, "|", f2)), data=data_used), adjust="fdr")
    list_of_tables[[paste0("PostHoc_", f1, "_by_", f2)]] <- format_posthoc_apa(res1)
    
    res2 <- pairs(emmeans(model, as.formula(paste("~", f2, "|", f1)), data=data_used), adjust="fdr")
    list_of_tables[[paste0("PostHoc_", f2, "_by_", f1)]] <- format_posthoc_apa(res2)
  } else {
    cat("      [Result] Interaction NS (or Single Factor) -> Reporting Main Effects (FDR).\n")
    for(f in factors) {
      res <- pairs(emmeans(model, as.formula(paste("~", f)), data=data_used), adjust="fdr")
      list_of_tables[[paste0("PostHoc_Main_", f)]] <- format_posthoc_apa(res)
    }
  }
  
  wb <- createWorkbook()
  for(sheet_name in names(list_of_tables)) {
    safe_sheet_name <- substr(gsub("[^A-Za-z0-9_]", "_", sheet_name), 1, 31)
    addWorksheet(wb, safe_sheet_name)
    writeData(wb, safe_sheet_name, list_of_tables[[sheet_name]])
    addStyle(wb, safe_sheet_name, createStyle(textDecoration="bold", border="Bottom"), rows=1, cols=1:ncol(list_of_tables[[sheet_name]]))
    setColWidths(wb, safe_sheet_name, cols=1:ncol(list_of_tables[[sheet_name]]), widths="auto")
  }
  
  # Dynamic naming with experiment version
  save_path <- file.path(out_dir, paste0("STATS_REPORT_", experiment_version, "_", label, ".xlsx"))
  saveWorkbook(wb, save_path, overwrite = TRUE)
  cat(paste0("      [Export] Final Excel Generated: ", basename(save_path), "\n"))
}


```

# 4. Data Import & Cleaning

```{r data-load}
if(!file.exists(path_input)) stop("Data file not found at: ", path_input)

cat(sprintf("\nLoading Trials Data for [%s] Pipeline...\n", experiment_version))

df_raw <- read_csv(path_input, show_col_types = FALSE)

clean_id <- function(x) {
  num_part <- as.numeric(str_extract(x, "\\d+"))
  sprintf("Vp%04d", num_part)
}

df_clean <- df_raw %>%
  mutate(
    participant_id = clean_id(participant_id),
    participant_id = factor(participant_id),
    
    ratio_val = Offers_You / (Offers_You + Offers_Other),
    offer_ratio = case_when(
      abs(ratio_val - 0.5) < 0.01 ~ "5:5",
      abs(ratio_val - 0.4) < 0.01 ~ "4:6",
      abs(ratio_val - 0.3) < 0.01 ~ "3:7",
      abs(ratio_val - 0.2) < 0.01 ~ "2:8",
      abs(ratio_val - 0.1) < 0.01 ~ "1:9",
      TRUE ~ NA_character_
    ),
    offer_ratio = factor(offer_ratio, levels = c("5:5", "4:6", "3:7", "2:8", "1:9")),
    
    offer_type = case_when(
      offer_ratio %in% c("5:5", "4:6") ~ "Fair",
      offer_ratio %in% c("2:8", "1:9") ~ "Unfair",
      TRUE ~ "Other"
    ),
    offer_type = factor(offer_type, levels = c("Fair", "Unfair", "Other")),
    
    is_reject = if_else(reaction == 2, 1L, 0L),
    logRT = log(RT),
    emotion = factor(emotion)
  ) %>%
  filter(!is.na(offer_ratio), !is.na(reaction), RT >= 150, RT <= 3000)

if(DEBUG_MODE) {
  # Warning: Aggressive subsetting restricts within-subject variance estimation.
  # Random effects structures may collapse to intercept-only during debugging.
  subs <- unique(df_clean$participant_id)[1:5]
  df_clean <- df_clean %>% filter(participant_id %in% subs)
  cat(">>> DEBUG MODE: Subset to 5 subjects.\n")
}

# CONTRASTS (CRITICAL)
contrasts(df_clean$emotion) <- contr.sum
contrasts(df_clean$offer_type) <- contr.sum
contrasts(df_clean$offer_ratio) <- contr.sum

cat("N Trials for Analysis:", nrow(df_clean), "\n")


```

# 5. Confirmatory Analysis: Offer Type (Fair vs. Unfair)

This section executes our primary hypothesis testing. The model initiates with a maximal zero-correlation parameterization structure to ensure convergence while protecting critical random slopes.

```{r analysis-type}
# Methodological Note: 
# High degrees of freedom limits are enforced to guarantee exact Satterthwaite 
# calculations for continuous RT data within computationally stable confines.
emmeans::emm_options(lmerTest.limit = 50000, pbkrtest.limit = 50000)
cat(">>> Configured emmeans: High precision DF enabled for Confirmatory Analysis.\n")

# Subset Data & Re-apply Contrasts (Protection against droplevels)
df_type <- df_clean %>% 
  filter(offer_type %in% c("Fair", "Unfair")) %>% 
  droplevels()

contrasts(df_type$offer_type) <- contr.sum
contrasts(df_type$emotion) <- contr.sum

# --- 1. Rejection Rate (GLMM - Binomial) ---
cat(sprintf("\n>>> Running: Confirmatory - Rejection Rate [%s] <<<\n", experiment_version))
m_type_rej <- run_robust_model(
  # Modified to Zero-Correlation Parameterization
  formula_str = "is_reject ~ emotion * offer_type + (1 | participant_id) + (0 + emotion | participant_id) + (0 + offer_type | participant_id) + (0 + emotion:offer_type | participant_id)",
  data = df_type, 
  family_type = "binomial", 
  fixed_terms = ~ emotion * offer_type
)
generate_report(m_type_rej, "Type_Rejection_Rate", c("emotion", "offer_type"), df_type)

# --- 2. Response Time (LMM - Gaussian) ---
cat(sprintf("\n>>> Running: Confirmatory - Response Time [%s] <<<\n", experiment_version))
m_type_rt <- run_robust_model(
  # Modified to Zero-Correlation Parameterization
  formula_str = "logRT ~ emotion * offer_type + (1 | participant_id) + (0 + emotion | participant_id) + (0 + offer_type | participant_id) + (0 + emotion:offer_type | participant_id)",
  data = df_type, 
  family_type = "gaussian", 
  fixed_terms = ~ emotion * offer_type
)
generate_report(m_type_rt, "Type_Response_Time", c("emotion", "offer_type"), df_type)

# ------------------------------------------------------------------------------
# --- 3. Robustness Check: Testing Sub-Maximal Structural Constraints ---
# ------------------------------------------------------------------------------
cat(sprintf("\n>>> Running: Robustness Check (Explicit Model Comparison) [%s] <<<\n", experiment_version))
robust_dir <- "Robustness_Check_Structural"

m_forced_1 <- glmmTMB(
  is_reject ~ emotion * offer_type + (1 + offer_type | participant_id),
  data = df_type, 
  family = binomial()
)
generate_report(m_forced_1, file.path(robust_dir, "Model_A_Structure"), c("emotion", "offer_type"), df_type)

m_forced_2 <- tryCatch({
  glmmTMB(
    is_reject ~ emotion * offer_type + (1 + emotion + offer_type | participant_id),
    data = df_type, 
    family = binomial()
  )
}, warning = function(w) {
  cat("   [Warning] Singular fit detected, applying ZCP fallback...\n")
  glmmTMB(
    is_reject ~ emotion * offer_type + (1 | participant_id) + (0 + emotion | participant_id) + (0 + offer_type | participant_id),
    data = df_type, 
    family = binomial()
  )
}, error = function(e) {
  cat("   [Error] Severe convergence failure.\n")
  return(NULL)
})

if(!is.null(m_forced_2)) {
  generate_report(m_forced_2, file.path(robust_dir, "Model_B_Structure"), c("emotion", "offer_type"), df_type)
  cat("\n   [INFO] Likelihood Ratio Test (Nested Structural Comparison):\n")
  lrt_results <- anova(m_forced_1, m_forced_2)
  print(lrt_results)
  
  lrt_out_path <- file.path(path_out_root, robust_dir, paste0("LRT_Model_Comparison_", experiment_version, ".txt"))
  capture.output(print(lrt_results), file = lrt_out_path)
}


```

# 6. Exploratory Analysis: Offer Ratio (Full Spectrum)

This section treats the 5-level continuous-like proxy (`offer_ratio`) strictly as a categorical interaction ($5 \times 5 = 25$ unique cells). Because precise variance-covariance matrix inversion across 25 factor combinations frequently triggers numerical singularity and memory exhaustion, we enforce ZCP structures combined with asymptotic approximation algorithms ($z$-tests).

```{r analysis-ratio}
# Methodological Note (Singularity Protection):
# Reducing the limit triggers asymptotic distributions (infinite DF) in `emmeans`, 
# bypassing computationally explosive Satterthwaite matrix inversions in high-dimensional grids.
emmeans::emm_options(lmerTest.limit = 3000, pbkrtest.limit = 3000)
cat(">>> Configured emmeans: Asymptotic approximations enabled for Exploratory Analysis.\n")

df_ratio <- df_clean %>% droplevels()
contrasts(df_ratio$offer_ratio) <- contr.sum
contrasts(df_ratio$emotion) <- contr.sum

# --- 1. Rejection Rate ---
cat(sprintf("\n>>> Running: Exploratory - Offer Ratio Rejection Rate [%s] <<<\n", experiment_version))
m_ratio_rej <- run_robust_model(
  # Modified to Zero-Correlation Parameterization for 5x5 design
  formula_str = "is_reject ~ emotion * offer_ratio + (1 | participant_id) + (0 + emotion | participant_id) + (0 + offer_ratio | participant_id) + (0 + emotion:offer_ratio | participant_id)",
  data = df_ratio, 
  family_type = "binomial", 
  fixed_terms = ~ emotion * offer_ratio
)
generate_report(m_ratio_rej, "Ratio_Rejection_Rate", c("emotion", "offer_ratio"), df_ratio)

# --- 2. Response Time ---
cat(sprintf("\n>>> Running: Exploratory - Offer Ratio Response Time [%s] <<<\n", experiment_version))
m_ratio_rt <- run_robust_model(
  # Modified to Zero-Correlation Parameterization for 5x5 design
  formula_str = "logRT ~ emotion * offer_ratio + (1 | participant_id) + (0 + emotion | participant_id) + (0 + offer_ratio | participant_id) + (0 + emotion:offer_ratio | participant_id)",
  data = df_ratio, 
  family_type = "gaussian", 
  fixed_terms = ~ emotion * offer_ratio
)
generate_report(m_ratio_rt, "Ratio_Response_Time", c("emotion", "offer_ratio"), df_ratio)


```

# 7. Exploratory Analysis III: Unfair Rejection RT

```{r analysis-unfair}
df_unfair <- df_clean %>% 
  filter(offer_type == "Unfair", is_reject == 1) %>% 
  droplevels()

if(nrow(df_unfair) > 50) {
  contrasts(df_unfair$emotion) <- contr.sum
  
  cat(sprintf("\n>>> Running: Exploratory - Unfair Rejection RT [%s] <<<\n", experiment_version))
  m_unfair <- run_robust_model(
    # Modified to Zero-Correlation Parameterization
    formula_str = "logRT ~ emotion + (1 | participant_id) + (0 + emotion | participant_id)",
    data = df_unfair,
    family_type = "gaussian",
    fixed_terms = ~ emotion
  )
  generate_report(m_unfair, "Unfair_Rejection_RT", c("emotion"), df_unfair)
} else {
  cat(sprintf("Skipped Unfair Analysis for %s (Insufficient Data: Model untestable)\n", experiment_version))
}


```

# 8. Session Info

```{r session}
sessionInfo()


```

