---
title: "Master Preprocessing Pipeline: UG EEG"
subtitle: "Optimized: Single-Pass Stimulus-Locked Extraction with Cluster-Based Permutation Tests"
author: "Project Maintainer"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: show
    theme: flatly
---

``` {r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# ==============================================================================
# 1. Environment and Global Configuration
# ==============================================================================

# Ensure required packages are installed and loaded
if(!require("pacman")) install.packages("pacman")
if(!require("here")) install.packages("here")
pacman::p_load(tidyverse, reticulate, readr, stringr, here, fs)

# -----------------------------------------------------------
# Method Configuration
# -----------------------------------------------------------
# Defines the preprocessing strategy for statistical analysis.
# TRUE  = Standard Method: Subtracts baseline mean from the epoch (traditional ERP).
# FALSE = Regression Method: No baseline subtraction. Pre-stimulus baseline 
#          activity is extracted as a covariate for LMMs (Recommended).
use_baseline_correction <- TRUE   

# -----------------------------------------------------------
# Baseline Parameters (Stimulus-Locked Only)
# -----------------------------------------------------------
use_full_prestim_baseline <- FALSE

# Construct the baseline argument for MNE-Python.
# NOTE: 'reticulate' handling of R lists vs. vectors is critical here.
# - R: list(NULL, 0) -> Python: [None, 0] -> MNE: (None, 0) [Correct]
# - R: c(NULL, 0)    -> Python: 0.0        -> MNE: Error       [Incorrect]
baseline_arg <- NULL

if (use_baseline_correction) {
  if (use_full_prestim_baseline) {
    # Baseline: Start of epoch to 0ms
    baseline_arg <- list(NULL, 0.0) 
  } else {
    # Baseline: -200ms to 0ms
    baseline_arg <- c(-0.2, 0.0)    
  }
} else {
  # Baseline: None (No correction applied)
  baseline_arg <- NULL 
}

# -----------------------------------------------------------
# Phase Control (Pipeline Stages)
# -----------------------------------------------------------
# Set to TRUE to execute the respective analysis phase.
run_offer_phase <- TRUE   # Stimulus-Locked (N170, FRN, P2, N400, LPP)
run_cpp_phase   <- FALSE  # Response-Locked (CPP) - Set to FALSE to skip

# -----------------------------------------------------------
# Path Definitions (Hierarchical & Dynamic)
# -----------------------------------------------------------

# A. Source Directories (Input)
path_py_pipeline_src <- here("python_modules", "hu-neuro-pipeline")
path_raw_eeg         <- here("data", "00_Raw_Input", "raw_all_cropped")
path_raw_log         <- here("data", "00_Raw_Input", "csv_all")

# B. Intermediate Processing Logs (Output)
path_csv_filtered    <- here("data", "01_Preprocessing_Logs", "csv_filtered")
path_csv_summary     <- here("data", "01_Preprocessing_Logs", "csv_summary")

# C. Pipeline Output Root
path_output_root     <- here("data", "02_Pipeline_Output")

# D. Dynamic Directory Naming based on Method
if (use_baseline_correction) {
  path_suffix <- "Standard_Baseline"
  method_folder <- "Method_Standard"
} else {
  path_suffix <- "No_Baseline"
  method_folder <- "Method_Regression"
}

# Sub-directory names
dir_stim_name  <- "Stimulus_Locked"    
dir_cpp_name   <- "Response_Locked"

# E. Destination Paths (Absolute)
path_dest_stim       <- file.path(path_output_root, method_folder, dir_stim_name)
path_dest_cpp        <- file.path(path_output_root, method_folder, dir_cpp_name)
path_dest_covariates <- file.path(path_output_root, "Covariates")
path_dest_baseline   <- file.path(path_output_root, "Baseline_Raw") 

# Report Paths
path_dest_report_stim <- file.path(path_dest_stim, "report")
path_dest_report_cpp  <- file.path(path_dest_cpp, "report")

# F. Directory Initialization
dirs_to_create <- c(
  path_csv_filtered, 
  path_csv_summary, 
  path_output_root,
  path_dest_stim, 
  path_dest_cpp, 
  path_dest_covariates,
  path_dest_baseline,
  path_dest_report_stim,
  path_dest_report_cpp
)
purrr::walk(dirs_to_create, ~dir.create(., showWarnings = FALSE, recursive = TRUE))



```

# 2. Python Environment Initialization

```{r Environment, include=FALSE}
# Initialize the conda environment for reticulate
use_condaenv("r-reticulate", required = TRUE)

# Pass the local pipeline source path from R to Python
py_pipeline_path <- path_py_pipeline_src

py_run_string("
import sys
import os
import importlib

# Logic to handle pipeline module reloading for development/updates
pipeline_modules = [key for key in list(sys.modules.keys()) if 'pipeline' in key]

# Inject local pipeline source into sys.path
local_path = r.py_pipeline_path
if os.path.exists(local_path):
    if local_path not in sys.path:
        sys.path.insert(0, local_path)
    print(f'Info: Using LOCAL pipeline source at: {local_path}')
else:
    print(f'Warning: Local path not found. Using system pipeline.')

try:
    import pipeline
    importlib.reload(pipeline) # Force reload to ensure latest code is used
    print(f'Info: Pipeline loaded from: {pipeline.__file__}')
except ImportError as e:
    print(f'Error: Could not import pipeline. Check path configuration. {e}')
")

# Import the pipeline module into R
pipeline_mod <- import("pipeline")



```

# 3. Log Preprocessing (Trial-Level and Summary Extraction)

```{r log-preprocessing}
orig_logs <- list.files(path_raw_log, pattern = "\\.txt$", full.names = TRUE)

cat("Processing", length(orig_logs), "log files...\n")

for (fpath in orig_logs) {
  # 1) Detect file encoding (UTF-16LE vs UTF-8) using Byte Order Mark (BOM)
  fb  <- file(fpath, "rb")
  bom <- readBin(fb, "raw", n = 2)
  close(fb)
  encoding <- if (length(bom) == 2 && identical(bom, as.raw(c(0xFF, 0xFE)))) "UTF-16LE" else "UTF-8"

  # 2) Read data with detected encoding
  df <- read_delim(
    fpath,
    delim = "\t",
    col_types = cols(),
    show_col_types = FALSE,
    locale = locale(encoding = encoding)
  )

  n <- nrow(df)

  # 3) Extract trial-level data 
  # Removes the last 3 lines (ratings) and Block 7 (practice/unused)
  df_trials <- df %>% 
    slice(1:(n-3)) %>% 
    filter(block != 7) %>% 
    mutate(emotion = str_extract(stim, "enj|dis|dom|neu|aff"))

  # 4) Extract summary / post-rating data (last 3 lines)
  df_summary <- df %>% slice((n-2):n)

  # 5) Save outputs
  out_name <- paste0(tools::file_path_sans_ext(basename(fpath)), ".csv")
  out_name_summary <- paste0(tools::file_path_sans_ext(basename(fpath)), "_summaryPostRating.csv")
    
  # Save cleaned trial logs
  write_csv(df_trials, file.path(path_csv_filtered, out_name))
  # Save summary ratings
  write_csv(df_summary, file.path(path_dest_covariates, out_name_summary))
}
cat("Log preprocessing complete.\n")



```

# 4. Condition Definitions (Shared Across Components)

```{r define-conditions}
# ==============================================================================
# Experimental Design & Condition Pooling Specifications
# ==============================================================================
# Fair categorization: Offers 5:5 and 6:4
# Unfair categorization: Offers 8:2 and 9:1
# Note: Offer 7:3 serves as a filler condition and is excluded from the pooled 
#       fairness contrasts to maximize signal-to-noise ratio.
# General Inclusion Criteria: Valid reaction (>0), RT between 150 and 3000 ms.

common_average_by <- list(
    
    # -------------------------------------------------------------------------
    # A. Raw Cell Conditions (5 Emotions x 5 Offers)
    # -------------------------------------------------------------------------
    # Maintained for granular extraction, single-trial analysis (LMM), or plotting.
    
    Face_enj_5_5 = "emotion=='enj' & Offers_Other==5 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_dis_5_5 = "emotion=='dis' & Offers_Other==5 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_dom_5_5 = "emotion=='dom' & Offers_Other==5 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_neu_5_5 = "emotion=='neu' & Offers_Other==5 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_aff_5_5 = "emotion=='aff' & Offers_Other==5 & reaction>0 & RT >= 150 & RT <= 3000",
    
    Face_enj_6_4 = "emotion=='enj' & Offers_Other==6 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_dis_6_4 = "emotion=='dis' & Offers_Other==6 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_dom_6_4 = "emotion=='dom' & Offers_Other==6 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_neu_6_4 = "emotion=='neu' & Offers_Other==6 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_aff_6_4 = "emotion=='aff' & Offers_Other==6 & reaction>0 & RT >= 150 & RT <= 3000",
    
    Face_enj_7_3 = "emotion=='enj' & Offers_Other==7 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_dis_7_3 = "emotion=='dis' & Offers_Other==7 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_dom_7_3 = "emotion=='dom' & Offers_Other==7 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_neu_7_3 = "emotion=='neu' & Offers_Other==7 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_aff_7_3 = "emotion=='aff' & Offers_Other==7 & reaction>0 & RT >= 150 & RT <= 3000",
    
    Face_enj_8_2 = "emotion=='enj' & Offers_Other==8 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_dis_8_2 = "emotion=='dis' & Offers_Other==8 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_dom_8_2 = "emotion=='dom' & Offers_Other==8 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_neu_8_2 = "emotion=='neu' & Offers_Other==8 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_aff_8_2 = "emotion=='aff' & Offers_Other==8 & reaction>0 & RT >= 150 & RT <= 3000",
    
    Face_enj_9_1 = "emotion=='enj' & Offers_Other==9 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_dis_9_1 = "emotion=='dis' & Offers_Other==9 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_dom_9_1 = "emotion=='dom' & Offers_Other==9 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_neu_9_1 = "emotion=='neu' & Offers_Other==9 & reaction>0 & RT >= 150 & RT <= 3000",
    Face_aff_9_1 = "emotion=='aff' & Offers_Other==9 & reaction>0 & RT >= 150 & RT <= 3000",

    # -------------------------------------------------------------------------
    # B. Main Effect Pooling (Orthogonal Dimensions)
    # -------------------------------------------------------------------------
    
    # 1. Main Effect of Fairness (Collapsing across Emotion)
    Grand_Fair   = "(emotion=='enj' | emotion=='dis' | emotion=='dom' | emotion=='neu' | emotion=='aff') & (Offers_Other==5 | Offers_Other==6) & reaction>0 & RT >= 150 & RT <= 3000",
    Grand_Unfair = "(emotion=='enj' | emotion=='dis' | emotion=='dom' | emotion=='neu' | emotion=='aff') & (Offers_Other==8 | Offers_Other==9) & reaction>0 & RT >= 150 & RT <= 3000",

    # 2. Main Effect of Emotion (Collapsing across Offer Ratios)
    All_Neu = "emotion=='neu' & reaction>0 & RT >= 150 & RT <= 3000",
    All_Dis = "emotion=='dis' & reaction>0 & RT >= 150 & RT <= 3000",
    All_Enj = "emotion=='enj' & reaction>0 & RT >= 150 & RT <= 3000",
    All_Dom = "emotion=='dom' & reaction>0 & RT >= 150 & RT <= 3000",
    All_Aff = "emotion=='aff' & reaction>0 & RT >= 150 & RT <= 3000",

    # -------------------------------------------------------------------------
    # C. Simple Effect Pooling (Emotion within Fairness Contexts)
    # -------------------------------------------------------------------------
    
    # Context: Unfair Offers (8:2 and 9:1)
    Face_dis_Unfair = "emotion=='dis' & (Offers_Other==8 | Offers_Other==9) & reaction>0 & RT >= 150 & RT <= 3000",
    Face_neu_Unfair = "emotion=='neu' & (Offers_Other==8 | Offers_Other==9) & reaction>0 & RT >= 150 & RT <= 3000",
    Face_enj_Unfair = "emotion=='enj' & (Offers_Other==8 | Offers_Other==9) & reaction>0 & RT >= 150 & RT <= 3000",
    Face_dom_Unfair = "emotion=='dom' & (Offers_Other==8 | Offers_Other==9) & reaction>0 & RT >= 150 & RT <= 3000",
    Face_aff_Unfair = "emotion=='aff' & (Offers_Other==8 | Offers_Other==9) & reaction>0 & RT >= 150 & RT <= 3000",

    # Context: Fair Offers (5:5 and 6:4)
    Face_dis_Fair = "emotion=='dis' & (Offers_Other==5 | Offers_Other==6) & reaction>0 & RT >= 150 & RT <= 3000",
    Face_neu_Fair = "emotion=='neu' & (Offers_Other==5 | Offers_Other==6) & reaction>0 & RT >= 150 & RT <= 3000",
    Face_enj_Fair = "emotion=='enj' & (Offers_Other==5 | Offers_Other==6) & reaction>0 & RT >= 150 & RT <= 3000",
    Face_dom_Fair = "emotion=='dom' & (Offers_Other==5 | Offers_Other==6) & reaction>0 & RT >= 150 & RT <= 3000",
    Face_aff_Fair = "emotion=='aff' & (Offers_Other==5 | Offers_Other==6) & reaction>0 & RT >= 150 & RT <= 3000"
)

# Helper function to archive key output files (e.g., trials.csv)
copy_trials_csv <- function(src_dir, dest_dir, new_filename = "trials.csv") {
  src_trials <- file.path(src_dir, "trials.csv")
  if (file.exists(src_trials)) {
    file.copy(src_trials, file.path(dest_dir, new_filename), overwrite = TRUE)
    cat(sprintf(">> Archived: %s/%s\n", basename(dest_dir), new_filename))
  } else {
    warning(sprintf("Source file not found: %s", src_trials))
  }
}



```

# 5. ERP Component Extraction and Statistical Testing

## 5.1 Stimulus-Locked Phase (Unified: N170, FRN, P2, N400, LPP)

Performs a **single-pass extraction** for component amplitudes and runs **Cluster-based Permutation Tests**.

```{r stimulus-locked-phase}
if (run_offer_phase) {

  # A. Define Destination
  out_stim <- path_dest_stim
  if (!dir.exists(out_stim)) dir.create(out_stim, recursive = TRUE)

  # --- FILE DETECTION ---
  stim_raw_files <- list.files(path_raw_eeg, pattern = "\\.(set|vhdr)$", full.names = TRUE, ignore.case = TRUE)
  if (length(stim_raw_files) == 0) stop("CRITICAL: No EEG files (.set or .vhdr) found in ", path_raw_eeg)

  cat(sprintf("\n=== Running Stimulus-Locked Extraction & Statistics ===\n"))
  cat(sprintf("Method: %s\n", path_suffix))
  cat(sprintf("Found %d raw files for processing.\n", length(stim_raw_files)))

  # B. Component Definition (For Single-Trial Amplitude Extraction)
  # Standard time windows for N170, FRN, P2, N400, and LPP
  erp_config <- tibble::tribble(
    ~comp_name,    ~t_min, ~t_max, ~roi_channels,
    "N170",        0.150,  0.200,  c("P7","P8","PO7","PO8"),
    "FRN",         0.250,  0.300,  c("F3","Fz","F4","FC1","FC2","Cz"),
    "P2",          0.200,  0.300,  c("PO3","POz","PO4","O1","Oz","O2"),
    "LPP_offer",   0.500,  0.800,  c("Pz","Cz","C1","C2","CP1","CP2"),
    "N400",        0.350,  0.450,  c("Fz","Cz","CPz","Pz")
  )
  
  # C. Conditional Baseline Extraction (Regression Method)
  if (!use_baseline_correction) {
    cat("   [Config] Adding matched baseline components (-200ms to 0ms) for covariate extraction...\n")
    baseline_config <- erp_config %>%
      mutate(comp_name = paste0("Baseline_", comp_name), t_min = -0.200, t_max = 0.000)
    final_config <- bind_rows(erp_config, baseline_config)
  } else {
    final_config <- erp_config
  }

  # Prepare Python Arguments for Component Extraction
  components_arg <- list(
    name = as.list(final_config$comp_name),
    tmin = as.list(final_config$t_min),
    tmax = as.list(final_config$t_max),
    roi  = final_config$roi_channels
  )

  # D. Permutation Test Configuration
  # Hierarchical statistical contrasts to test experimental hypotheses.
  
  perm_contrasts_list <- list(
    # 1. Main Effect of Fairness (Validation of UG paradigm)
    c('Grand_Unfair', 'Grand_Fair'),
    
    # 2. Main Effect of Emotion (Manipulation check for facial stimuli)
    c('All_Dis', 'All_Neu'),
    c('All_Enj', 'All_Neu'),
    c('All_Dom', 'All_Neu'),
    c('All_Aff', 'All_Neu'),

    # 3. Simple Effects: Emotional modulation within Unfair context
    c('Face_dis_Unfair', 'Face_neu_Unfair'),  
    c('Face_enj_Unfair', 'Face_neu_Unfair'),  
    c('Face_dom_Unfair', 'Face_neu_Unfair'),  
    c('Face_aff_Unfair', 'Face_neu_Unfair'),

    # 4. Control Comparisons: Emotional modulation within Fair context
    c('Face_dis_Fair', 'Face_neu_Fair'),
    c('Face_enj_Fair', 'Face_neu_Fair'),
    c('Face_dom_Fair', 'Face_neu_Fair'),
    c('Face_aff_Fair', 'Face_neu_Fair')
  )

  # E. Execute Pipeline (Single Pass)
  # - Extracts single-trial amplitudes for `trials.csv`
  # - Runs permutation tests for `clusters.csv`
  res_stim <- pipeline_mod$group_pipeline(
    raw_files        = stim_raw_files,   
    log_files        = path_csv_filtered,
    output_dir       = out_stim,     
    epochs_dir       = file.path(out_stim, "epochs"), 
    
    # Preprocessing Parameters
    ica_method       = "fastica",
    ica_n_components = 0.99,
    triggers         = c(10:89, 150:169),
    bad_channels     = "auto",
    highpass_freq    = 0.05,
    lowpass_freq     = 30.0,
    reject_peak_to_peak = 200.0,
    baseline         = baseline_arg, 
    
    # Task 1: Component Amplitude Extraction
    components       = components_arg, 
    average_by       = common_average_by,
    
    # Task 2: Cluster-Based Permutation Tests
    # Note: Window expanded to 0.150 - 0.800 ms to capture early N170/N200/FRN onset and late LPP dynamics.
    perm_contrasts   = perm_contrasts_list,
    perm_tmin        = 0.150,  
    perm_tmax        = 0.800,  
    perm_channels    = NULL    # Default: Whole-brain search
  )
  
  # F. Archive Baseline Values (If applicable)
  if (!use_baseline_correction) {
      out_bl_archive <- file.path(path_dest_baseline, "Stimulus_Locked_Values")
      if(!dir.exists(out_bl_archive)) dir.create(out_bl_archive, recursive=TRUE)
      copy_trials_csv(out_stim, out_bl_archive, "baseline_values.csv")
  }
}



```

## 5.2 Response-Locked Phase (CPP)

This section extracts the Central Parietal Positivity (CPP).
**Note:** Execution is controlled by the `run_cpp_phase` flag.

```{r response-locked-phase}
if (run_cpp_phase) {

  out_cpp <- path_dest_cpp
  if (!dir.exists(out_cpp)) dir.create(out_cpp, recursive = TRUE)
  
  # --- STEP 1: Detect Available Files ---
  raw_files_found <- list.files(path_raw_eeg, pattern = "\\.(set|vhdr)$", full.names = TRUE, ignore.case = TRUE)
  log_files_found <- list.files(path_csv_filtered, pattern = "\\.csv$", full.names = TRUE)
  
  if (length(raw_files_found) == 0) stop("CRITICAL: No EEG files found for CPP phase.")
  
  cat(sprintf("\n=== Running Response-Locked Extraction (CPP) ===\n"))

  # --- STEP 2: Create Aligned Logs (Numeric ID Matching) ---
  path_csv_cpp_aligned <- file.path(path_output_root, "01_Preprocessing_Logs", "csv_cpp_aligned")
  if (!dir.exists(path_csv_cpp_aligned)) dir.create(path_csv_cpp_aligned, recursive = TRUE)
  
  final_raw_list <- c()
  final_log_list <- c()
  log_ids <- as.integer(str_extract(basename(log_files_found), "\\d+"))
  
  for (raw_path in raw_files_found) {
    raw_fname <- basename(raw_path)
    eeg_id <- as.integer(str_extract(raw_fname, "\\d+"))
    match_idx <- which(log_ids == eeg_id)
    
    if (length(match_idx) == 1) {
      src_log <- log_files_found[match_idx]
      df_temp <- read_csv(src_log, show_col_types = FALSE)
      df_cpp <- df_temp %>% filter(reaction > 0)
      
      dest_fname <- paste0(tools::file_path_sans_ext(raw_fname), ".csv")
      dest_log   <- file.path(path_csv_cpp_aligned, dest_fname)
      write_csv(df_cpp, dest_log)
      
      final_raw_list <- c(final_raw_list, raw_path)
      final_log_list <- c(final_log_list, dest_log)
    }
  }

  if (length(final_raw_list) == 0) stop("No valid Raw-Log pairs found for CPP.")

  # --- STEP 3: Configuration & Execution ---
  roi_cpp <- c("Pz","Cz","C1","C2","CP1","CP2")
  cpp_components <- list(name = list("CPP"), tmin = list(-0.30), tmax = list(0.05), roi  = list(roi_cpp))
  
  # Convert to R lists for Python compatibility
  py_raw_files <- as.list(final_raw_list)
  py_log_files <- as.list(final_log_list)

  res_cpp <- pipeline_mod$group_pipeline(
    raw_files        = py_raw_files,
    log_files        = py_log_files,
    output_dir       = out_cpp,
    epochs_dir       = file.path(out_cpp, "epochs"), 
    
    ica_method       = "fastica",
    ica_n_components = 0.99,
    triggers         = c(1, 2), 
    epochs_on_missing = 'ignore',        
    bad_channels     = "auto",
    highpass_freq    = 0.05,
    lowpass_freq     = 30.0,
    epochs_tmin      = -0.9,             
    epochs_tmax      = 0.5,
    baseline         = NULL, 
    reject_peak_to_peak = 200.0,
    components       = cpp_components,
    average_by       = common_average_by
  )

  copy_trials_csv(out_cpp, path_dest_cpp)
} else {
  cat("\n[INFO] Skipping Response-Locked (CPP) Phase as configured.\n")
}



```

# 6. Summary of Generated Files

```{r summary}
cat("\n========================================\n")
cat("          PREPROCESSING COMPLETE          \n")
cat("========================================\n")
cat("Method Strategy: ", path_suffix, "\n")
cat("Output Root:     ", path_output_root, "\n\n")

cat("1. Stimulus-Locked (N170, FRN, P2, N400, LPP): \n")
if (run_offer_phase) {
  cat("   -> Data (Single Trials): ", file.path(path_dest_stim, "trials.csv"), "\n")
  cat("   -> Stats (Permutation):  ", file.path(path_dest_stim, "group_clusters.csv"), "\n")
  cat("   -> Epochs:               ", file.path(path_dest_stim, "epochs"), "\n")
} else {
  cat("   -> [SKIPPED]\n")
}

cat("2. Response-Locked (CPP): \n")
if (run_cpp_phase) {
  cat("   -> Data (Single Trials): ", file.path(path_dest_cpp, "trials.csv"), "\n")
} else {
  cat("   -> [SKIPPED]\n")
}

if (!use_baseline_correction) {
  cat("\n[INFO] Regression Method Active: Waveforms are NOT baseline corrected.\n")
}
cat("========================================\n")



```
